Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-07-07 paper.tex
New scatter plots
Adding takahashi matched figure

\subsection{D$_{st}$ Events}
Two event indicators are looked at in this study. The first is looking for a drop in DST below the threshhold of $-40nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe an event until $D_{st}$ passes back above the $-40nT$ threshold. This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours. Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after. Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40nT$. The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average. The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average. Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack. A subset of longer duration events will be looked at later.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-27day.eps}
\caption{One-day and 27-day averaged $D_{st}$ storms}
\label{DailyAverages}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day-nof107.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-27day-nof107.eps}
\caption{One-day and 27-day averaged $D_{st}$ storms with $F_{10.7}$ dependence removed}
\label{DailyAveragesNoF107}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.7]{paperfigures/ccplot.eps}
\caption{Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ }
\label{ccplot}
\end{figure}
\clearpage

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{Storms}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dd12.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-d80.eps}
\caption{(a) Same as \ref{fig:Storms}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours. (b) Same as \ref{fig:Storms}(b) except for constrain that $D_{st}$ crossed below $-80 nT$.}
\label{Mspec}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-md12.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $\rho_{eq}$ stayed above 50~nT for at least 12~hours. (b) Same as \ref{fig:Storms}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
\label{Dspec}
\end{figure}
\clearpage

>>>>

\subsection{D$_{st}$ Events}
Two event indicators are looked at in this study. The first is looking for a drop in DST below the threshold of $-40nT$ specified in \cite{Takahashi2010}, dubbed the "onset", and then considering the timeframe an event until $D_{st}$ passes back above the $-40nT$ threshold. This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours. Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after. Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40nT$. The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average. The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average. Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack. A subset of longer duration events will be looked at later.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day.eps}
\includegraphics[scale=0.5]{paperfigures/stormavs-dst-day-50.eps}
\caption{One-day averaged $D_{st}$ storms at thresholds of $-40nT$ and $-50nT$}
\label{DailyAverages}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
\includegraphics[scale=0.42]{paperfigures/DSTvsMD.eps}
\includegraphics[scale=0.42]{paperfigures/DstMDAllData.eps}
\caption{(a) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (b) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. (c) All data of $D_{st}$ and $\rho_{eq}$ }
\label{ccplot}
\end{figure}
\clearpage

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dst.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-mass.eps}
\caption{(a) Average of solar wind and near-Earth measurements around the time $D_{st}$ crossed below -40~nT onset. (b) Same as (a) except around time intervals where mass density crossed above $40 amu/cm^3$.  The bottom panel shows the number of mass density data points that were used for the average.}
\label{Storms}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-dd12.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-d80.eps}
\caption{(a) Same as \ref{fig:Storms}(a) except with constraint that $D_{st}$ stayed below -40~nT for at least 12~hours. (b) Same as \ref{fig:Storms}(b) except for constrain that $D_{st}$ crossed below $-80 nT$.}
\label{Mspec}
\end{figure}
\clearpage

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/stormavs-md12.eps}
\includegraphics[scale=0.45]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as \ref{fig:MassStorm}(a) except with constraint that $\rho_{eq}$ stayed above 50~nT for at least 12~hours. (b) Same as \ref{fig:Storms}(b) except for constrain that mass density crossed above $70 amu/cm^3$.}
\label{Dspec}
\end{figure}
\clearpage
